Finalised versions of normalisation and threshold

### 2020-07-23 simulations_MMPD6.Rmd
simulation graph

```{r initial, echo = FALSE, cache = FALSE, include = FALSE}
options("knitr.graphics.auto_pdf" = TRUE)
library(knitr)
library(tidyverse)
library(lubridate)
library(lvplot)
library(ggridges)
library(viridis)
library(tsibble)
library(gravitas)
library(ggpubr)
library(readr)
opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE, comment = "#>",
  fig.path = "figure/", fig.align = "center", fig.show = "hold",
  cache = FALSE, cache.path = "cache/",
  out.width = ifelse(is_html_output(), "100%", "\\textwidth")
)
knitr::opts_knit$set(root.dir = here::here())
```

@@

```{r normalisation_work}
smart_harmony %>% mutate(lev = facet_levels*x_levels) %>% ggplot(aes(x = lev, y = r)) +geom_point()
smart_harmony %>% mutate(lev = facet_levels*x_levels, r_MMPD = row_number()) %>% ggplot(aes(x = lev, y = r_MMPD)) +geom_line()
```

@@

@@

@@

>>>>

```{r initial, echo = FALSE, cache = FALSE, include = FALSE}
options("knitr.graphics.auto_pdf" = TRUE)
library(knitr)
library(tidyverse)
library(lubridate)
library(lvplot)
library(ggridges)
library(viridis)
library(tsibble)
library(gravitas)
library(ggpubr)
library(readr)

opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE, comment = "#>",
  fig.path = "figure/", fig.align = "center", fig.show = "hold",
  cache = TRUE, cache.path = "cache/",
  out.width = ifelse(is_html_output(), "100%", "\\textwidth")
)
knitr::opts_knit$set(root.dir = here::here())
```

@@

```{r normalisation_work}
smart_harmony %>% mutate(lev = facet_levels*x_levels) %>% ggplot(aes(x = lev, y = r)) + geom_line()
smart_harmony %>% mutate(lev = facet_levels*x_levels, r_MMPD = row_number()) %>% ggplot(aes(x = lev, y = r_MMPD)) +geom_line()
```

@@

```{r scene1}
library(readr)
library(ggplot2)
sim_data1 <- read_rds("sim_data1.rds")

sim_data1 %>%
  dplyr::filter(name==1) %>%
  ggplot(aes(x = Var2, y = sim_data)) + geom_boxplot() + facet_wrap(~Var1)

global_harmony_iter1 <- read_rds("data/global_harmony_iter1.rds")

global_harmony_iter1 %>% kable()
```

@@

```{r scene2}
library(readr)
library(ggplot2)
sim_data2 <- read_rds("sim_data2.rds")

sim_data2 %>%
  dplyr::filter(name==1) %>%
  ggplot(aes(x = Var2, y = sim_data)) + geom_boxplot() + facet_wrap(~Var1)

global_harmony_iter2 <- read_rds("data/global_harmony_iter2.rds")

global_harmony_iter2 %>% kable()
```

@@

```{r scene3}
library(readr)
library(ggplot2)

sim_data3 <- read_rds("sim_data3.rds")

sim_data3 %>%
  dplyr::filter(name==1) %>%
  ggplot(aes(x = Var2, y = sim_data)) + geom_boxplot() + facet_wrap(~Var1)

sim_data3 %>%
  dplyr::filter(name==4) %>%
  ggplot(aes(x = Var2, y = sim_data)) + geom_boxplot() + facet_wrap(~Var1)

global_harmony_iter3 <- read_rds("data/global_harmony_iter3.rds")

global_harmony_iter3 %>% kable()
```
